---
title: "Pentathlon III: Next Product to Buy Modeling"
output: html_document
---

* Team-lead gitlab id:
* Team-lead gitlab username:
* Group number:
* Group name:
* Team member names:

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## load radiant packages if neededi
if (!exists("r_environment")) library(radiant)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

## Setup

Please complete this Rmarkdown document by answering the questions in `pentathlon-nptb.pdf` on Dropbox (week8/readings/). The code block below will load the data you need. Please DO NOT change the code used to load the data. Create an HTML file with all your results and comments and push both the Rmarkdown and HTML file to GitLab when you are done. As always, all results MUST be reproducible (i.e., the TA and I must be able to recreate the HTML from the R-markdown file without changes or errors).

Good luck!

```{r}
## Loading the data from Dropbox/MGTA455-2018/data/
pentathlon_nptb_wrk <- readr::read_rds(file.path(radiant.data::find_dropbox(), "MGTA455-2018/data/pentathlon_nptb.rds"))
if (!exists("r_data")) r_data <- list()
r_data[["pentathlon_nptb_wrk"]] <- readr::read_rds(file.path(find_dropbox(), "MGTA455-2018/data/pentathlon_nptb.rds"))
r_data[["pentathlon_nptb_wrk"]] <- readr::read_rds(file.path(find_dropbox(), "MGTA455-2018/data/pentathlon_nptb.rds"))
```

## Question answers

Loading libraries
```{r}
library(radiant)
library(ranger)
install.packages("randomForest")
library(randomForest)
library(readr)
library(dplyr)
library(rpart)
library(rpart.plot)
library(xgboost)
library(Matrix)
library(radiant)
library(methods)
library(caret)
library(data.table)
install.packages("mlr")
library(mlr)
```

## Dividing training, validation, representative datasets:
```{r}
r_data[["pentathlon_nptb_train"]]  <- r_data[["pentathlon_nptb_wrk"]] %>% filter(training==1)
r_data[["pentathlon_nptb_validation"]] <- r_data[["pentathlon_nptb_wrk"]] %>% filter(training==0)
r_data[["pentathlon_nptb_representative"]] <- r_data[["pentathlon_nptb_wrk"]] %>% filter(is.na(training))

## note training and valid both have 50% buyers and 50% non buyers, but rep sample has 1% buyers and 99% non buyers.
```


## Logistic Regression  Base Model:


Logistic

a) Regression:
```{r}
result_logistic <- logistic(
  dataset = "pentathlon_nptb_train", 
  rvar = "buyer", 
  evar = c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  ), 
  lev = "yes", 
  int = c(
    "message:age", "message:gender", 
    "message:income", "message:education", 
    "message:children", "message:freq_endurance", 
    "message:freq_strength", 
    "message:freq_water", 
    "message:freq_team", 
    "message:freq_backcountry", 
    "message:freq_winter", 
    "message:freq_racquet"
  ), 
  check = "standardize"
)
summary(result_logistic, sum_check = "confint")
```


```{r}
## training:
pentathlon_nptb_train <- as.data.frame(r_data[["pentathlon_nptb_train"]])
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='endurance'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_endurance")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='strength'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_strength")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='water'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_water")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='team'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_team")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='backcountry'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_backcountry")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='winter'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_winter")

pred <- predict(result_logistic, pred_data = "pentathlon_nptb_train", pred_cmd = "message='racquet'")
store(pred, data = "pentathlon_nptb_train", name = "p_logit_racquet")





## Validation:
pentathlon_nptb_validation <- as.data.frame(r_data[["pentathlon_nptb_validation"]])

# Probability function for validation
# predict probabilities for all seven categories of messages and storing them
predict_probabilities <- function(){
temp <<- pentathlon_nptb_validation$message

pentathlon_nptb_validation$message <<-  "endurance"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_endurance")

pentathlon_nptb_validation$message<<- "strength"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_strength")

pentathlon_nptb_validation$message<<- "water"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_water")

pentathlon_nptb_validation$message<<- "team"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_team")

pentathlon_nptb_validation$message<<- "backcountry"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_backcountry")

pentathlon_nptb_validation$message<<- "winter"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_winter")

pentathlon_nptb_validation$message<<- "racquet"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "p_logit_racquet")


pentathlon_nptb_validation$message <<- temp

}

predict_probabilities()






## Representative:
pentathlon_nptb_representative <- as.data.frame(r_data[["pentathlon_nptb_representative"]])
predict_probabilities_representatives <- function(){
temp <<- pentathlon_nptb_representative$message

pentathlon_nptb_representative$message <<-  "endurance"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_endurance")

pentathlon_nptb_representative$message<<- "strength"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_strength")

pentathlon_nptb_representative$message<<- "water"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_water")

pentathlon_nptb_representative$message<<- "team"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_team")

pentathlon_nptb_representative$message<<- "backcountry"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_backcountry")

pentathlon_nptb_representative$message<<- "winter"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_winter")

pentathlon_nptb_representative$message<<- "racquet"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_racquet")


pentathlon_nptb_representative$message <<- temp

}

predict_probabilities_representatives()


pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(pAdj_logit_endurance = p_logit_endurance/ ((p_logit_endurance + (1-p_logit_endurance)*(1-0.01)/0.01)),
         pAdj_logit_strength = p_logit_strength/ ((p_logit_strength + (1-p_logit_strength)*(1-0.01)/0.01)),
         pAdj_logit_water = p_logit_water/ ((p_logit_water + (1-p_logit_water)*(1-0.01)/0.01)),
         pAdj_logit_team = p_logit_team/ ((p_logit_team + (1-p_logit_team)*(1-0.01)/0.01)),
         pAdj_logit_backcountry = p_logit_backcountry/ ((p_logit_backcountry + (1-p_logit_backcountry)*(1-0.01)/0.01)),
         pAdj_logit_winter = p_logit_winter/ ((p_logit_winter + (1-p_logit_winter)*(1-0.01)/0.01)),
         pAdj_logit_racquet = p_logit_racquet/((p_logit_racquet + (1-p_logit_racquet)*(1-0.01)/0.01))
         )
```

# Whom to send email

# Question 1
```{r}

# which department will send email depending upon only probabilities
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(to_offer = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(p_logit_endurance, p_logit_strength, p_logit_water, p_logit_team,p_logit_backcountry, p_logit_winter,p_logit_racquet )])

#pentathlon_nptb_representative:

# which department will send email depending upon only probabilities
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(to_offer = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(pAdj_logit_endurance, pAdj_logit_strength, pAdj_logit_water, pAdj_logit_team,pAdj_logit_backcountry, pAdj_logit_winter,pAdj_logit_racquet )])



```


Calculate the probability of purchase for each of the customers after sending each category of messages. Find out the message category for which the probability of purchase is maximum for each of the customers. the determined message will be that corresponding message category which has been mentioned in "to_offer" column.


# Question 2

```{r}

result <- pivotr(
  dataset = "pentathlon_nptb_representative", 
  cvars = "to_offer",
  normalize = "total",
  tabsort = "desc(n)"
)
summary(result, perc=TRUE)

```



# Question 3

Linear regression to predict Order size:

```{r}
pentathlon_nptb_train_bought <- filter(pentathlon_nptb_train, buyer=="yes")
result_linear <- regress(
  dataset = "pentathlon_nptb_train_bought", 
  rvar = "total_os", 
  evar = c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  ), 
  
  int = c(
  "message:income"
    
  ), 
  check = "standardize"
)
summary(result_linear, sum_check = c("rmse", "vif"))
# store(result, name = "residuals_reg")
```

# Ordersize prediction function
```{r}
#=============================================
# predict total ordersize for all seven categories of messages and storing them
predict_OS <- function(){
  
pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='endurance'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_endurance")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='strength'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_strength")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='water'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_water")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='team'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_team")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='backcountry'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_backcountry")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='winter'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_winter")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='racquet'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_racquet")
}


predict_OS_representative <- function(){
  
pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='endurance'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_endurance")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='strength'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_strength")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='water'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_water")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='team'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_team")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='backcountry'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_backcountry")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='winter'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_winter")

pred <- predict(result_linear, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='racquet'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_racquet")
}

predict_OS_representative()


```


# Profit function
```{r}
# few ordersize came negative- make them zero
# pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(predict_os_endurance= ifelse(predict_os_endurance<0,0,predict_os_endurance),predict_os_strength= ifelse(predict_os_strength<0,0,predict_os_strength),predict_os_water= ifelse(predict_os_water<0,0,predict_os_water),predict_os_team= ifelse(predict_os_team<0,0,predict_os_team),predict_os_backcountry= ifelse(predict_os_backcountry<0,0,predict_os_backcountry), predict_os_winter= ifelse(predict_os_winter<0,0,predict_os_winter),predict_os_racquet= ifelse(predict_os_racquet<0,0,predict_os_racquet))

profit <- function(){

# To whom mail to be sent based on profit
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(to_offer_profit = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(predict_endurancei*predict_os_endurance, predict_strengthi*predict_os_strength, predict_wateri*predict_os_water, predict_teami*predict_os_team,predict_backcountryi*predict_os_backcountry, predict_winteri*predict_os_winter,predict_racqueti*predict_os_racquet)])


# What is the expected profit from each customer
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(profit_expected = 0.40*pmax(predict_endurancei*predict_os_endurance, predict_strengthi*predict_os_strength, predict_wateri*predict_os_water, predict_teami*predict_os_team,predict_backcountryi*predict_os_backcountry, predict_winteri*predict_os_winter,predict_racqueti*predict_os_racquet))

#Total expected profit
Model_profit <- sum(pentathlon_nptb_validation$profit_expected)

#total actual profit against which the above should be compared

Original_profit <- sum(pentathlon_nptb_validation$total_os*.4)

###****Profit is less than random message which is weird... means both the model (predicted probabilities and ordersize estimation) requires finetuning.***###
return(Model_profit)

}



profit_reprentative <- function(){

# To whom mail to be sent based on profit
pentathlon_nptb_representative <<- pentathlon_nptb_representative %>% mutate(to_offer_profit = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(pAdj_logit_endurance*predict_os_endurance, pAdj_logit_strength*predict_os_strength, pAdj_logit_water*predict_os_water, pAdj_logit_team*predict_os_team,pAdj_logit_backcountry*predict_os_backcountry, pAdj_logit_winter*predict_os_winter,pAdj_logit_racquet*predict_os_racquet)])

# What is the expected profit from each customer
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(profit_expected = 0.40*pmax(pAdj_logit_endurance*predict_os_endurance, pAdj_logit_strength*predict_os_strength, pAdj_logit_water*predict_os_water, pAdj_logit_team*predict_os_team,pAdj_logit_backcountry*predict_os_backcountry, pAdj_logit_winter*predict_os_winter,pAdj_logit_racquet*predict_os_racquet))

#Total expected profit
Model_profit <- sum(pentathlon_nptb_representative$profit_expected)

#total actual profit against which the above should be compared



###****Profit is less than random message which is weird... means both the model (predicted probabilities and ordersize estimation) requires finetuning.***###
return(Model_profit)

}
PROFIT <- profit_reprentative()

Original_profit <- sum(pentathlon_nptb_representative$total_os*.4)

```

# Question 3

#Approach


# Question 4

```{r}

result <- pivotr(
  dataset = "pentathlon_nptb_representative", 
  cvars = "to_offer_profit",
  normalize = "total",
  tabsort = "desc(n)"
)
summary(result, perc=TRUE)

```

# Average profit per emailed customer = `r round(PROFIT/100000,2)`

# Question 6
```{r}
Endurance <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_endurance*pentathlon_nptb_representative$predict_os_endurance)

Strength <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_strength*pentathlon_nptb_representative$predict_os_strength)

Water <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_water*pentathlon_nptb_representative$predict_os_water)

Team <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_team*pentathlon_nptb_representative$predict_os_team)

Backcountry <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_backcountry*pentathlon_nptb_representative$predict_os_backcountry)

Winter <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_winter*pentathlon_nptb_representative$predict_os_winter)

Racquet <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_racquet*pentathlon_nptb_representative$predict_os_racquet)

Endurance
Strength
Water
Team
Backcountry
Winter
Racquet

```




============================================================================================================================









## XGBoost Model (NOT FINALIZED-- INCOMPLETE):
```{r}
train  <- r_data[["pentathlon_nptb_wrk"]] %>% filter(training==1)
validation <- r_data[["pentathlon_nptb_wrk"]] %>% filter(training==0)
xgb_pentathlon_nptb_rep <- r_data[["pentathlon_nptb_wrk"]] %>% filter(is.na(training))
```

```{r}
xgb_pentathlon_nptb_train <- train[,c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  )]
xgb_pentathlon_nptb_validation <-validation[,c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  )]
```



  rvar = "buyer", 
  evar = c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  ), 
  lev = "yes", 
  int = c(
    "message:age", "message:gender", 
    "message:income", "message:education", 
    "message:children", "message:freq_endurance", 
    "message:freq_strength", 
    "message:freq_water", 
    "message:freq_team", 
    "message:freq_backcountry", 
    "message:freq_winter", 
    "message:freq_racquet"
  ),
  
```{r}
##XGBoost
validation$buyer <- ifelse(validation$buyer == "yes", 1,0)
train$buyer <- ifelse(train$buyer == "yes", 1,0)

dtrain <- xgb.DMatrix(data=data.matrix(xgb_pentathlon_nptb_train), label=train$buyer)
dvalidation <- xgb.DMatrix(data=data.matrix(xgb_pentathlon_nptb_validation), label=validation$buyer)

watchlist <- list(validation=dvalidation, train=dtrain)

param <- list(
  objective = "binary:logistic",
  eta = 0.0025,
  gamma= 0.10,
  #max_depth = 8,
  subsample = 0.30,
  colsample_bytree = .75,
  scale_pos_weight = 0.97,
  min_child_weight = 30,
  max_delta_step = 7,
  lambda = 20
)

xgb_model <- xgb.train( params = param,
                  data = dtrain,
                  nfold=3,
                  eval_metric="logloss",
                  print_every_n = 50,
                  nrounds = 4400,
                  num_boost_round=10,
                  seed = 123,
                  verbose = 1,
                  early_stopping_rounds = 500,
                  watchlist = watchlist
)

pred <- predict(xgb_model, data.matrix(xgb_pentathlon_nptb_validation))
r_data[["pentathlon_nptb_validation"]]$xgb_prob <- pred

imp <- xgb.importance (feature_names = colnames(dtrain),model = xgb_model)
xgb.plot.importance (importance_matrix = imp)
```


```{r}
xgb_grid_1 = expand.grid(
nrounds = 1000,
eta = c(0.01, 0.001, 0.0001),
max_depth = c(2, 4, 6, 8, 10),
gamma = 1
)
 
# pack the training control parameters
xgb_trcontrol_1 = trainControl(
method = "cv",
number = 5,
verboseIter = TRUE,
returnData = FALSE,
returnResamp = "all",                                                        # save losses across all models
classProbs = TRUE,                                                           # set to TRUE for AUC to be computed
summaryFunction = twoClassSummary,
allowParallel = TRUE
)
 
# train the model for each parameter combination in the grid,
#   using CV to evaluate
xgb_train_1 = train(
x = as.matrix(df_train %>%
select(-SeriousDlqin2yrs)),
y = as.factor(df_train$SeriousDlqin2yrs),
trControl = xgb_trcontrol_1,
tuneGrid = xgb_grid_1,
method = "xgbTree"
)
 
# scatter plot of the AUC against max_depth and eta
ggplot(xgb_train_1$results, aes(x = as.factor(eta), y = max_depth, size = ROC, color = ROC)) +
geom_point() +
theme_bw() +
scale_size_continuous(guide = "none")
```



#### using Caret

```{r}
#set variable names
setcol <- c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  )

train_0<-r_data[["pentathlon_nptb_wrk"]] %>% filter(training==1)
test_0<- r_data[["pentathlon_nptb_wrk"]] %>% filter(training==0)
rep_0<- r_data[["pentathlon_nptb_wrk"]] %>% filter(is.na(training))

train_labels <- as.numeric(train_0$buyer)-1
test_labels <- as.numeric(test_0$buyer)-1
rep_labels <- as.numeric(rep_0$buyer)-1

train <-train_0[,setcol]
test <-test_0[,setcol]
rep <-rep_0[,setcol]

# one-hot-encoding categorical features
ohe_feats = c('message', 'age', 'gender')

dummies_train <- dummyVars(~ message +  age + gender, data = train)
dummies_test <- dummyVars(~ message +  age + gender, data = test)
dummies_rep <- dummyVars(~ message +  age + gender, data = rep)

df_all_oh_train <- as.data.frame(predict(dummies_train, newdata = train))
df_all_oh_test <- as.data.frame(predict(dummies_test, newdata = test))
df_all_oh_rep <- as.data.frame(predict(dummies_rep, newdata = rep))

## train preprocessing:
df_train_combined <- cbind(train[,-c(which(colnames(train) %in% ohe_feats))],df_all_oh_train)
df_train_combined$age_30 <- as.numeric(ifelse(df_train_combined[,"age.< 30"] < 0,1,0))
df_train_combined$age_31_44 <- as.numeric(ifelse(df_train_combined[,"age.30 to 44"] < 0,1,0))
df_train_combined$age_45_59 <- as.numeric(ifelse(df_train_combined[,"age.45 to 59"] < 0,1,0))
df_train_combined$age_60 <- as.numeric(ifelse(df_train_combined[,"age.>= 60"] < 0,1,0))


df_test_combined <- cbind(test[,-c(which(colnames(test) %in% ohe_feats))],df_all_oh_test)
df_test_combined$age_30 <- as.numeric(ifelse(df_test_combined[,"age.< 30"] < 0,1,0))
df_test_combined$age_31_44 <- as.numeric(ifelse(df_test_combined[,"age.30 to 44"] < 0,1,0))
df_test_combined$age_45_59 <- as.numeric(ifelse(df_test_combined[,"age.45 to 59"] < 0,1,0))
df_test_combined$age_60 <- as.numeric(ifelse(df_test_combined[,"age.>= 60"] < 0,1,0))

df_rep_combined <- cbind(rep[,-c(which(colnames(rep) %in% ohe_feats))],df_all_oh_rep)
df_rep_combined$age_30 <- as.numeric(ifelse(df_rep_combined[,"age.< 30"] < 0,1,0))
df_rep_combined$age_31_44 <- as.numeric(ifelse(df_rep_combined[,"age.30 to 44"] < 0,1,0))
df_rep_combined$age_45_59 <- as.numeric(ifelse(df_rep_combined[,"age.45 to 59"] < 0,1,0))
df_rep_combined$age_60 <- as.numeric(ifelse(df_rep_combined[,"age.>= 60"] < 0,1,0))

#preparing matrix 
dtrain <- xgb.DMatrix(data = data.matrix(df_train_combined),label = train_labels) 
dtest <- xgb.DMatrix(data = data.matrix(df_test_combined),label=test_labels)
drep <- xgb.DMatrix(data = data.matrix(df_rep_combined),label=rep_labels)

#default parameters
params <- list(
  booster = "gbtree", 
  objective = "binary:logistic", 
  eta=0.003, 
  gamma=0, 
  max_depth=6, 
  min_child_weight=1, 
  subsample=1, 
  colsample_bytree=1)


watchlist <- list(validation=dtest, train=dtrain)


# param <- list(
#   objective = "binary:logistic",
#   eta = 0.0025,
#   gamma= 0.10,
#   #max_depth = 8,
#   subsample = 0.30,
#   colsample_bytree = .75,
#   scale_pos_weight = 0.97,
#   min_child_weight = 30,
#   max_delta_step = 7,
#   lambda = 20
# )

xgbcv <- xgb.cv( 
  params = params, 
  data = dtrain, 
  nrounds = 1000, 
  nfold = 4, 
  showsd = T, 
  stratified = T, 
  print.every.n = 10, 
  early.stop.round = 200, 
  maximize = F)
##best iteration = 79


min(xgbcv$test.error.mean)


xgb_model <- xgb.train( params = params,
                  data = dtrain,
                  nfold=3,
                  eval_metric="error",
                  print_every_n = 50,
                  nrounds = 4400,
                  num_boost_round=10,
                  seed = 123,

                  verbose = 1,
                  early_stopping_rounds = 500,
                  watchlist = watchlist
)

xgbpred <- predict(xgb_model, dtest, type ="classification")


## error rate
err <- mean(as.numeric(xgbpred > 0.5) != test_labels)
print(paste("test-error=", err))


## Confusion Matrix
prediction <- as.numeric(xgbpred > 0.5)
print(head(prediction))
confusionMatrix (prediction, test_labels)

#view variable importance plot
mat <- xgb.importance (feature_names = colnames(dtrain),model = xgb_model)
xgb.plot.importance (importance_matrix = mat[1:20]) 




# auc_xgb <- max(xgb_model$results$ROC)
# 
# plot(xgb_model)
# summary(xgb_model)



```



## predicting customized messages:
```{r}
pentathlon_nptb_train  <- as.data.frame(r_data[["pentathlon_nptb_wrk"]] )%>% filter(training==1)
pentathlon_nptb_validation <- as.data.frame(r_data[["pentathlon_nptb_wrk"]]) %>% filter(training==0)
pentathlon_nptb_representative <- as.data.frame(r_data[["pentathlon_nptb_wrk"]]) %>% filter(is.na(training))


## Validation:
temp <<- pentathlon_nptb_validation$message

pentathlon_nptb_validation$message <-  "endurance"
dtest <- xgb.DMatrix(data = data.matrix(df_test_combined),label=test_labels)
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_endurance <- pred


pentathlon_nptb_validation$message <- "strength"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_strength <- pred


pentathlon_nptb_validation$message <- "water"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_water <- pred


pentathlon_nptb_validation$message <- "team"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_team <- pred


pentathlon_nptb_validation$message <- "backcountry"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_backcountry <- pred


pentathlon_nptb_validation$message <- "winter"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_winter <- pred


pentathlon_nptb_validation$message <- "racquet"
pred <- predict(xgb_model, dtest)
pentathlon_nptb_validation$p_xgb_racquet <- pred



pentathlon_nptb_validation$message <- temp




## representative:
temp <<- pentathlon_nptb_representative$message

pentathlon_nptb_representative$message <<-  "endurance"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_endurance")

pentathlon_nptb_representative$message<<- "strength"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_strength")

pentathlon_nptb_representative$message<<- "water"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_water")

pentathlon_nptb_representative$message<<- "team"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_team")

pentathlon_nptb_representative$message<<- "backcountry"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_backcountry")

pentathlon_nptb_representative$message<<- "winter"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_winter")

pentathlon_nptb_representative$message<<- "racquet"
pred <- predict(result_logistic, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "p_logit_racquet")


pentathlon_nptb_representative$message <<- temp
```
