---
title: "Pentathlon III:Next Product to Buy Modeling"
author: "Team 12"
date: "2/28/2018"
output: html_document
---
* Team-lead GitLab id: 1530157
* Team-lead GitLab username:rms-swchakra
* Group number:12
* Group name: Team 12
* Team member names: Asis, Swagata, Zongxian, Qiuyu, Jieyu

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## load radiant packages if neededi
if (!exists("r_environment")) library(radiant)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

```{r}
## Loading the data from Dropbox/MGTA455-2018/data/
pentathlon_nptb_wrk <- readr::read_rds(file.path(radiant.data::find_dropbox(), "MGTA455-2018/data/pentathlon_nptb.rds"))
```

split the data into training,testing and representative samples
```{r}
pentathlon_nptb_train <- filter(pentathlon_nptb_wrk, training==1)

pentathlon_nptb_validation <- filter(pentathlon_nptb_wrk, training==0)

pentathlon_nptb_representative <- filter(pentathlon_nptb_wrk, representative==1)

```


## Logistic Regression
```{r}
result <- logistic(
  dataset = "pentathlon_nptb_train", 
  rvar = "buyer", 
  evar = c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  ), 
  lev = "yes", 
  int = c(
    "message:age", "message:gender", 
    "message:income", "message:education", 
    "message:children", "message:freq_endurance", 
    "message:freq_strength", 
    "message:freq_water", 
    "message:freq_team", 
    "message:freq_backcountry", 
    "message:freq_winter", 
    "message:freq_racquet"
  )#, 
  #check = "standardize"
)
 summary(result)

```

Check the AUC of the logistic model. The AUC is around 88.3%.

```{r}
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_logit")

result_cf <- confusion(
  dataset = "pentathlon_nptb_validation", 
  pred = "predict_logit", 
  rvar = "buyer", 
  lev = "yes", 
  train = "All"
)
summary(result_cf)

```

# Probability function
```{r}
# predict probabilities for all seven categories of messages and storing them
predict_probabilities <- function(){
  
temp <<- pentathlon_nptb_validation$message

pentathlon_nptb_validation$message <<-  "endurance"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_endurancei")

pentathlon_nptb_validation$message<<- "strength"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_strengthi")

pentathlon_nptb_validation$message<<- "water"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_wateri")

pentathlon_nptb_validation$message<<- "team"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_teami")

pentathlon_nptb_validation$message<<- "backcountry"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_backcountryi")

pentathlon_nptb_validation$message<<- "winter"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_winteri")

pentathlon_nptb_validation$message<<- "racquet"
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_racqueti")


pentathlon_nptb_validation$message <<- temp

}

predict_probabilities()

predict_probabilities_representatives <- function(){

temp <- pentathlon_nptb_representative$message
  
pentathlon_nptb_representative$message<<- "endurance"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_endurancei")

pentathlon_nptb_representative$message<<- "strength"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_strengthi")

pentathlon_nptb_representative$message<<- "water"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_wateri")

pentathlon_nptb_representative$message<<- "team"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_teami")

pentathlon_nptb_representative$message<<- "backcountry"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_backcountryi")

pentathlon_nptb_representative$message<<- "winter"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_winteri")

pentathlon_nptb_representative$message<<- "racquet"
pred <- predict(result, pred_data = "pentathlon_nptb_representative")
store(pred, data = "pentathlon_nptb_representative", name = "predict_racqueti")

pentathlon_nptb_representative$message <<- temp
}


predict_probabilities_representatives()

pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(pAdj_logit_endurance = predict_endurancei/ ((predict_endurancei + (1-predict_endurancei)*(1-0.01)/0.01)),
         pAdj_logit_strength = predict_strengthi/ ((predict_strengthi + (1-predict_strengthi)*(1-0.01)/0.01)),
         pAdj_logit_water = predict_wateri/ ((predict_wateri + (1-predict_wateri)*(1-0.01)/0.01)),
         pAdj_logit_team = predict_teami/ ((predict_teami + (1-predict_teami)*(1-0.01)/0.01)),
         pAdj_logit_backcountry = predict_backcountryi/ ((predict_backcountryi + (1-predict_backcountryi)*(1-0.01)/0.01)),
         pAdj_logit_winter = predict_winteri/ ((predict_winteri + (1-predict_winteri)*(1-0.01)/0.01)),
         pAdj_logit_racquet = predict_racqueti/((predict_racqueti + (1-predict_racqueti)*(1-0.01)/0.01))
         )


```



# Whom to send email

# Question 1
```{r}

# which department will send email depending upon only probabilities
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(to_offer = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(predict_endurancei, predict_strengthi, predict_wateri, predict_teami,predict_backcountryi, predict_winteri,predict_racqueti )])

#pentathlon_nptb_representative
    
# which department will send email depending upon only probabilities
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(to_offer = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(pAdj_logit_endurance, pAdj_logit_strength, pAdj_logit_water, pAdj_logit_team,pAdj_logit_backcountry, pAdj_logit_winter,pAdj_logit_racquet )])



```


Calculate the probability of purchase for each of the customers after sending each category of messages. Find out the message category for which the probability of purchase is maximum for each of the customers. the determined message will be that corresponding message category which has been mentioned in "to_offer" column.

、
# Question 2
```{r}

result <- pivotr(
  dataset = "pentathlon_nptb_representative", 
  cvars = "to_offer",
  normalize = "total",
  tabsort = "desc(n)"
)
summary(result, perc=TRUE)

```


# Linear regression to estimate ordersize
```{r}
pentathlon_nptb_train_bought <- filter(pentathlon_nptb_train, buyer=="yes")

result <- regress(
  dataset = "pentathlon_nptb_train_bought", 
  rvar = "total_os", 
  evar = c("message","age", "gender", "income", "education", 
    "children", "freq_endurance","freq_strength","freq_water","freq_backcountry", "freq_winter", "freq_racquet", "freq_winter"
  ), 
  int = c(
    "message:income"
    
  ), 
  check = "standardize"
)
summary(result)
```

# Ordersize prediction function
```{r}
#install.packages("Metrics")
library(Metrics)
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
# store(result, name = "residuals_reg")
store(pred, data = "pentathlon_nptb_validation", name = "predict_reg")
rmse(pentathlon_nptb_validation$total_os,pentathlon_nptb_validation$predict_reg)
auc(pentathlon_nptb_validation$total_os,pentathlon_nptb_validation$predict_reg)
#=============================================
# predict total ordersize for all seven categories of messages and storing them
predict_OS <- function(){
  
pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='endurance'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_endurance")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='strength'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_strength")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='water'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_water")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='team'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_team")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='backcountry'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_backcountry")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='winter'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_winter")

pred <- predict(result, pred_data = "pentathlon_nptb_validation", pred_cmd = "message='racquet'")
store(pred, data = "pentathlon_nptb_validation", name = "predict_os_racquet")
}


predict_OS_representative <- function(){
  
pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='endurance'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_endurance")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='strength'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_strength")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='water'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_water")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='team'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_team")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='backcountry'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_backcountry")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='winter'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_winter")

pred <- predict(result, pred_data = "pentathlon_nptb_representative", pred_cmd = "message='racquet'")
store(pred, data = "pentathlon_nptb_representative", name = "predict_os_racquet")
}

predict_OS_representative()


```


# Profit function
```{r}
# few ordersize came negative- make them zero
# pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(predict_os_endurance= ifelse(predict_os_endurance<0,0,predict_os_endurance),predict_os_strength= ifelse(predict_os_strength<0,0,predict_os_strength),predict_os_water= ifelse(predict_os_water<0,0,predict_os_water),predict_os_team= ifelse(predict_os_team<0,0,predict_os_team),predict_os_backcountry= ifelse(predict_os_backcountry<0,0,predict_os_backcountry), predict_os_winter= ifelse(predict_os_winter<0,0,predict_os_winter),predict_os_racquet= ifelse(predict_os_racquet<0,0,predict_os_racquet))

profit <- function(){

# To whom mail to be sent based on profit
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(to_offer_profit = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(predict_endurancei*predict_os_endurance, predict_strengthi*predict_os_strength, predict_wateri*predict_os_water, predict_teami*predict_os_team,predict_backcountryi*predict_os_backcountry, predict_winteri*predict_os_winter,predict_racqueti*predict_os_racquet)])


# What is the expected profit from each customer
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(profit_expected = 0.40*pmax(predict_endurancei*predict_os_endurance, predict_strengthi*predict_os_strength, predict_wateri*predict_os_water, predict_teami*predict_os_team,predict_backcountryi*predict_os_backcountry, predict_winteri*predict_os_winter,predict_racqueti*predict_os_racquet))

#Total expected profit
Model_profit <- sum(pentathlon_nptb_validation$profit_expected)

#total actual profit against which the above should be compared

Original_profit <- sum(pentathlon_nptb_validation$total_os*.4)

###****Profit is less than random message which is weird... means both the model (predicted probabilities and ordersize estimation) requires finetuning.***###
return(Model_profit)

}



profit_reprentative <- function(){

# To whom mail to be sent based on profit
pentathlon_nptb_representative <<- pentathlon_nptb_representative %>% mutate(to_offer_profit = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(pAdj_logit_endurance*predict_os_endurance, pAdj_logit_strength*predict_os_strength, pAdj_logit_water*predict_os_water, pAdj_logit_team*predict_os_team,pAdj_logit_backcountry*predict_os_backcountry, pAdj_logit_winter*predict_os_winter,pAdj_logit_racquet*predict_os_racquet)])

# What is the expected profit from each customer
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(profit_expected = 0.40*pmax(pAdj_logit_endurance*predict_os_endurance, pAdj_logit_strength*predict_os_strength, pAdj_logit_water*predict_os_water, pAdj_logit_team*predict_os_team,pAdj_logit_backcountry*predict_os_backcountry, pAdj_logit_winter*predict_os_winter,pAdj_logit_racquet*predict_os_racquet))

#Total expected profit
Model_profit <- sum(pentathlon_nptb_representative$profit_expected)

#total actual profit against which the above should be compared



###****Profit is less than random message which is weird... means both the model (predicted probabilities and ordersize estimation) requires finetuning.***###
return(Model_profit)

}
PROFIT <- profit_reprentative()

Original_profit <- sum(pentathlon_nptb_representative$total_os*.4)

```


# Question 3

#Approach


# Question 4

```{r}

result <- pivotr(
  dataset = "pentathlon_nptb_representative", 
  cvars = "to_offer_profit",
  normalize = "total",
  tabsort = "desc(n)"
)
summary(result, perc=TRUE)

```

# Average profit per emailed customer = `r round(PROFIT/100000,2)`

# Question 6
```{r}
Endurance <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_endurance*pentathlon_nptb_representative$predict_os_endurance)

Strength <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_strength*pentathlon_nptb_representative$predict_os_strength)

Water <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_water*pentathlon_nptb_representative$predict_os_water)

Team <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_team*pentathlon_nptb_representative$predict_os_team)

Backcountry <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_backcountry*pentathlon_nptb_representative$predict_os_backcountry)

Winter <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_winter*pentathlon_nptb_representative$predict_os_winter)

Racquet <- mean(0.4*pentathlon_nptb_representative$pAdj_logit_racquet*pentathlon_nptb_representative$predict_os_racquet)

Endurance
Strength
Water
Team
Backcountry
Winter
Racquet

```


# Neural Network_probabilities
```{r}
#NN
## Build the model

result <- nn(
  dataset = "pentathlon_nptb_train", 
  rvar = "buyer", 
  evar = c(
    "message", "age", "gender", "income", "education", "children", 
    "freq_endurance", "freq_strength", "freq_water", "freq_team", 
    "freq_backcountry", "freq_winter", "freq_racquet"
  ), 
  lev = "yes", 
  size = 5, 
  seed = 1234
)
summary(result, prn = TRUE)
pred <- predict(result, pred_data = "pentathlon_nptb_validation")
store(pred, data = "pentathlon_nptb_validation", name = "predict_nn5")


## The AUC is 89% in this case.
result <- confusion(
  dataset = "pentathlon_nptb_validation", 
  pred = "predict_nn5", 
  rvar = "buyer", 
  lev = "yes", 
  train = "All"
)
summary(result)


## Make predictions
## Validation dataset
predict_probabilities()

predict_probabilities_representatives()



```


# GBM Model
```{r}
#GBM
## GBM
## Build and train the model
library(caret)
library(tidyverse)
ctrl <- trainControl(
  method = "cv",
  classProbs = T,
  number = 5,
  selectionFunction = "best",
  summaryFunction = twoClassSummary,
  verboseIter = T)

gbm_model <- train(
  buyer~ message+ age+ gender+ income+ education+ children+freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+
    +freq_winter + freq_racquet,
  data = pentathlon_nptb_train,
  method = "gbm",
  trControl = ctrl,
  metric = "ROC",
  verbose = T)

#saveRDS(gbm_model, "gbm_model.rds")
gbm_model <- read_rds("gbm_model.rds")

auc_gbm <- max(gbm_model$results$ROC)

plot(gbm_model)
summary(gbm_model)

## Make predictions
## Validation dataset
for (i in 1:7){
  predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
}
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="endurance")
pentathlon_nptb_validation$gbm_end_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="strength")
pentathlon_nptb_validation$gbm_strg_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="water")
pentathlon_nptb_validation$gbm_water_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="team")
pentathlon_nptb_validation$gbm_team_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="backcountry")
pentathlon_nptb_validation$gbm_backct_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="winter")
pentathlon_nptb_validation$gbm_winter_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% mutate(message="racquet")
pentathlon_nptb_validation$gbm_rac_prob <- predict(gbm_model,pentathlon_nptb_validation,type = "prob")[,'yes']

pentathlon_nptb_validation <- pentathlon_nptb_validation %>% 
  mutate(profit_endurance_gbm = 0.4*predict_os_endurance*gbm_end_prob,
         profit_strength_gbm = 0.4*predict_os_strength*gbm_strg_prob,
         profit_water_gbm = 0.4*predict_os_water*gbm_water_prob,
         profit_team_gbm = 0.4*predict_os_team*gbm_team_prob,
         profit_backcountry_gbm = 0.4*predict_os_backcountry*gbm_backct_prob,
         profit_winter_gbm = 0.4*predict_os_winter*gbm_winter_prob,
         profit_racquet_gbm = 0.4*predict_os_racquet*gbm_rac_prob
  )
# Select the maximum profit
pentathlon_nptb_validation <- pentathlon_nptb_validation %>% 
  mutate(to_offer_dept_gbm = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(profit_endurance_gbm, profit_strength_gbm, profit_water_gbm, profit_team_gbm,profit_backcountry_gbm, profit_winter_gbm,profit_racquet_gbm )]) %>% 
  mutate(profit_max_gbm = pmax(profit_endurance_gbm, profit_strength_gbm, profit_water_gbm, profit_team_gbm,profit_backcountry_gbm, profit_winter_gbm,profit_racquet_gbm ))
# Check the total profit predicted
t1_gbm <- sum(pentathlon_nptb_validation$profit_max_gbm)
t2 <- sum(pentathlon_nptb_validation$total_os)
t2*.4
t1_gbm/t2

## Representative dataset
message <- c("endurance","strength","water","team","backcountry","winter","racquet")
for (i in 1:7){
  pred_profit <- predict(result_profit, pred_data = "pentathlon_nptb_representative", pred_cmd = paste0("message=","'",message[i],"'"))
  store(pred_profit,data="pentathlon_nptb_representative",name=paste0("gbm_",message[i],"_prob"))
}

pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="endurance")
pentathlon_nptb_representative$gbm_end_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="strength")
pentathlon_nptb_representative$gbm_strg_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="water")
pentathlon_nptb_representative$gbm_water_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="team")
pentathlon_nptb_representative$gbm_team_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="backcountry")
pentathlon_nptb_representative$gbm_backct_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="winter")
pentathlon_nptb_representative$gbm_winter_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% mutate(message="racquet")
pentathlon_nptb_representative$gbm_rac_prob <- predict(gbm_model,pentathlon_nptb_representative,type = "prob")[,'yes']

pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(profit_endurance_gbm = 0.4*predict_os_endurance*gbm_end_prob,
         profit_strength_gbm = 0.4*predict_os_strength*gbm_strg_prob,
         profit_water_gbm = 0.4*predict_os_water*gbm_water_prob,
         profit_team_gbm = 0.4*predict_os_team*gbm_team_prob,
         profit_backcountry_gbm = 0.4*predict_os_backcountry*gbm_backct_prob,
         profit_winter_gbm = 0.4*predict_os_winter*gbm_winter_prob,
         profit_racquet_gbm = 0.4*predict_os_racquet*gbm_rac_prob
  )


pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(pAdj_representative_endurance = gbm_end_prob/ ((gbm_end_prob + (1-gbm_end_prob)*(1-0.01)/0.01)),
         pAdj_representative_strength = gbm_strg_prob/ ((gbm_strg_prob + (1-gbm_strg_prob)*(1-0.01)/0.01)),
         pAdj_representative_water = gbm_water_prob/ ((gbm_water_prob + (1-gbm_water_prob)*(1-0.01)/0.01)),
         pAdj_representative_team = gbm_team_prob/ ((gbm_team_prob + (1-gbm_team_prob)*(1-0.01)/0.01)),
         pAdj_representative_backcountry = gbm_backct_prob/ ((gbm_backct_prob + (1-gbm_backct_prob)*(1-0.01)/0.01)),
         pAdj_representative_winter = gbm_winter_prob/ ((gbm_winter_prob + (1-gbm_winter_prob)*(1-0.01)/0.01)),
         pAdj_representative_racquet = gbm_rac_prob/((gbm_rac_prob + (1-gbm_rac_prob)*(1-0.01)/0.01))
  )

pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(profit_endurance_gbmi = 0.4*predict_os_endurance*pAdj_representative_endurance,
         profit_strength_gbmi = 0.4*predict_os_strength*pAdj_representative_strength,
         profit_water_gbmi = 0.4* pAdj_representative_water,
         profit_team_gbmi = 0.4*predict_os_team*pAdj_representative_team,
         profit_backcountry_gbmi = 0.4*predict_os_backcountry*pAdj_representative_backcountry,
         profit_winter_gbmi = 0.4*predict_os_winter*pAdj_representative_winter,
         profit_racquet_gbmi = 0.4*predict_os_racquet*pAdj_representative_racquet
  )


# Select the maximum profit
pentathlon_nptb_representative <- pentathlon_nptb_representative %>% 
  mutate(to_offer_dept_gbm = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(profit_endurance_gbm, pAdj_representative_strength, profit_water_gbm, profit_team_gbm,profit_backcountry_gbm, profit_winter_gbm,profit_racquet_gbm )],
         profit_max_gbm = pmax(profit_endurance_gbm, profit_strength_gbm, profit_water_gbm, profit_team_gbm,profit_backcountry_gbm, profit_winter_gbm,profit_racquet_gbm ),
         to_offer_dept_gbmi = c("endurance","strength","water","team","backcountry","winter","racquet")[which.pmax(pAdj_representative_endurance, profit_strength_gbm,  pAdj_representative_water, pAdj_representative_team,pAdj_representative_backcountry, pAdj_representative_winter,pAdj_representative_racquet )],
         profit_max_gbmi = pmax(profit_endurance_gbmi, profit_strength_gbmi, profit_water_gbmi, profit_team_gbmi,profit_backcountry_gbmi, profit_winter_gbmi,profit_racquet_gbmi ))

```


Monthly basis expeectations or ranking would not change much-..
Also, as emails are on weekly basis there is no clarity how many emails should be sent by which 
department(of the two highest probable)

This is not done at random...will go into reinforcemnet loop.....they should at least keep few customers at random..


